Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2017-09-25 documentation/userguide.tex
Minor updates to the documentation

This software assumes that you have set several environment variables:
\begin{itemize}
  \item \texttt{AMREX\_HOME}, the location of the \amrex\ code's top-level directory
  \item \texttt{CASTRO\_DIR}, the location of the \castro\ code's top-level directory
  \item \texttt{WDMERGER\_HOME}, the location of this software's top-level directory
  \item \texttt{MICROPHYSICS\_DIR}, the location of the \texttt{Microphysics} code's top-level directory
\end{itemize}

@@

A note on machine compatibility: this software is currently only developed and tested on
machines that run Linux and come with the common GNU flavors of most pieces of software
like \texttt{sed}. We do not guarantee that this software will work out of the box on OS X
or other Unix derivatives; however, we generally try to avoid GNU-specific options, so that 
trying to run this software on OS X will not be too painful. With that being said, this 
software does heavily rely on \texttt{bash} and at present there are no plans to maintain
compatibility with any other shell.

@@

\castro\ includes full self-gravity with the Poisson equation, as well as the ability to perform a
simulation in a rotating reference frame with fixed rotation period. By default the $z$ axis will 
be the rotation axis, with the stars initially aligned along the $x$ axis. We select the 
orbital period of the system, and the masses of the \textit{primary} (more massive) and 
\textit{secondary} (less massive) white dwarfs. We then use Kepler's third law to determine the 
appropriate initial orbital distance. The center of mass of the system corresponds with the center 
of the domain, which is the origin; the domain is $1.024 \times 10^{10}\ \text{cm}$ wide in each 
coordinate direction, so that each dimension runs from $-5.12 \times 10^{9}\ \text{cm}$ to 
$+5.12 \times 10^{9}\ \text{cm}$. In a rotating reference frame, we set the stars at rest. 
We can instead run a simulation in the inertial reference frame. To make it equivalent, we
start all zones in the domain with a velocity corresponding to the equivalent rotating 
reference frame velocity. This means that the stars will be synchronously rotating (though we
may relax this assumption in future work).

@@

for period in 25.0 50.0 75.0 100.0
do
  dir=results/period$period/
  castro_rotational_period=$period
  stop_time=$period
  run $dir $nprocs $walltime
done
\end{lstlisting}%$
This will create the subdirectories \texttt{results/period25.0} through \texttt{results/period100.0}
and in each directory the inputs file will have the corresponding \texttt{castro.rotational\_period}.
Each job will stop after one rotational period has been completed. At the end, the script will automatically move all 
output files (checkpoints, plot files, diagnostics)
to the \texttt{output/} subdirectory of that problem location, and on supported HPC systems will also copy these 
files to the long-term storage system (see Section \ref{sec:archiving} for more details). 
Generally our analysis scripts expect all the output to be in the 
\texttt{output/} subdirectory. Also, if the machine crashes before your run completes, running \texttt{bash run.sh}
again will automatically restart your job from the most recent checkpoint.

@@

This project was started as the Ph.D. dissertation project for Max Katz at Stony Brook University. 
Michael Zingale is Max's primary thesis advisor. Correspondence and requests for information 
about this software should be directed to them; their e-mail addresses are maximilian.katz@stonybrook.edu
and michael.zingale@stonybrook.edu, respectively. Alan Calder and Doug Swesty at Stony Brook are 
also co-investigators on this project. The \castro\ code was developed primarily at the 
Lawrence Berkeley National Laboratory. Staff there that have contributed directly and 
indirectly to this project include Ann Almgren, John Bell, Weiqun Zhang, Andy Nonaka, and Vince Beckner.

>>>>

This software assumes that you have set several environment variables:
\begin{itemize}
  \item \texttt{AMREX\_HOME}, the location of the \amrex\ code's top-level directory
  \item \texttt{CASTRO\_HOME}, the location of the \castro\ code's top-level directory
  \item \texttt{WDMERGER\_HOME}, the location of this software's top-level directory
  \item \texttt{MICROPHYSICS\_HOME}, the location of the \texttt{Microphysics} code's top-level directory
\end{itemize}

@@

A note on machine compatibility: this software is currently only developed and tested on
machines that run Linux and come with the common GNU flavors of most pieces of software
like \texttt{sed}. We do not guarantee that this software will work out of the box on OS X
or other Unix derivatives; however, we have generally tried to avoid GNU-specific options
where possible. This software does heavily rely on \texttt{bash} and at present there are
no plans to maintain compatibility with any other shell.

@@

\castro\ includes full self-gravity with the Poisson equation, as well as the ability to perform a
simulation in a rotating reference frame with fixed rotation period. By default the $z$ axis will 
be the rotation axis, with the stars initially aligned along the $x$ axis. We select the 
orbital period of the system, and the masses of the \textit{primary} (more massive) and 
\textit{secondary} (less massive) white dwarfs. We then use Kepler's third law to determine the 
appropriate initial orbital distance. The center of mass of the system corresponds with the center 
of the domain, which is the origin. In a rotating reference frame, we set the stars at rest. 
We can instead run a simulation in the inertial reference frame. To make it equivalent, we
start all zones in the domain with a velocity corresponding to the equivalent rotating 
reference frame velocity. This means that the stars will be synchronously rotating (though we
may relax this assumption in the future).

@@

for period in 25.0 50.0 75.0 100.0
do
  dir=results/period$period/
  castro_rotational_period=$period
  stop_time=$period
  run
done
\end{lstlisting}%$
This will create the subdirectories \texttt{results/period25.0} through \texttt{results/period100.0}
and in each directory the inputs file will have the corresponding \texttt{castro.rotational\_period}.
Each job will stop after one rotational period has been completed. At the end, the script will automatically move all 
output files (checkpoints, plot files, diagnostics)
to the \texttt{output/} subdirectory of that problem location, and on supported HPC systems will also copy these 
files to the long-term storage system (see Section \ref{sec:archiving} for more details). 
Generally our analysis scripts expect all the output to be in the 
\texttt{output/} subdirectory. Also, if the machine crashes before your run completes, running \texttt{bash run.sh}
again will automatically restart your job from the most recent checkpoint.

@@

This project was started as the Ph.D. dissertation project for Max Katz at Stony Brook University;
Max now continues work on it, though he is no longer physically at Stony Brook.
Michael Zingale is the other main contact at Stony Brook. Correspondence and requests for information 
about this software should be directed to them; their e-mail addresses are maximilian.katz@stonybrook.edu
and michael.zingale@stonybrook.edu, respectively. Alan Calder and Doug Swesty at Stony Brook are 
also co-investigators on this project. The \castro\ code was developed primarily at the 
Lawrence Berkeley National Laboratory. Staff there that have contributed directly and 
indirectly to this project include Ann Almgren, John Bell, Weiqun Zhang, Andy Nonaka, and Vince Beckner.
